Analyzing Fairness: Race, Recidivism, and the COMPAS Algorithm

### 2022-04-15 final_metrics_analysis.Rmd
Finalizing plots and plot captions

```{python exploratory race bar plot}
# barplot of race
sns.countplot(x="race", data=df_viz, palette=[blue, orange])
plt.title('Race Distribution (White and Black individuals only)')
```

```{python exploratory age by race plot}
# age distribution by race
ax = sns.kdeplot(x="age", hue="race", data=df_viz);
kdeline = ax.lines[0]
mean_fem = df_viz.groupby('race').age.median()[0]
xs = kdeline.get_xdata()
ys = kdeline.get_ydata()
height_fem = np.interp(mean_fem, xs, ys)
ax.vlines(mean_fem, 0, height_fem, color=blue, ls=':')

mean_m = df_viz.groupby('race').age.median()[1]
height_m = np.interp(mean_m, xs, ys)
ax.vlines(mean_m, 0, height_m, color=orange, ls=':')

>>>>

```{python exploratory race bar plot}
# barplot of race
sns.countplot(x="race", data=df_viz, palette=workshop_palette)
plt.title('Race Distribution (White and Black individuals only)')
```

```{python exploratory age by race plot}
# age distribution by race
ax = sns.kdeplot(x="age", hue="race", data=df_viz, palette=workshop_palette);
kdeline = ax.lines[0]
mean_black = df_viz.groupby('race').age.median()[0]
xs = kdeline.get_xdata()
ys = kdeline.get_ydata()
height_black = np.interp(mean_black, xs, ys)
ax.vlines(mean_black, 0, height_black, color=purple, ls=':')

mean_white = df_viz.groupby('race').age.median()[1]
height_white = np.interp(mean_white, xs, ys)
ax.vlines(mean_white, 0, height_white, color=green, ls=':')
